Montreal Real Estate Pricing \\ {\normalsize Code available at: \url{https://github.com/mike-n-7/ML4}}

### 2014-12-04 Paper/paper.tex
Added abstract.

\maketitle
\begin{abstract}

>>>>

\maketitle
\begin{abstract}
	One of the most important stages most people go through at one point in their lives involves buying or selling a home.  Real estate is the largest asset the average person will ever own and many times functions as not only a shelter but also an investment. The more information parties on either side of the transaction can obtain, the better their decision will be and the chances of losing large sums of money will decrease. While many models have been applied to this market over the years, not many have investigated the role municipal data about infrastructure has on pricing these homes. Through the use of data available through the city of Montreal and a snapshot of the real estate market on the island through select agencies, we look to investigate the impact leveraging municipal data can have on pricing and compare the performance of Linear Regression, Lasso Regression and K nearest neighbours in this setting. Results show that much of the city data played little in the output of the learners used and that poorer performance by the algorithms suggests the truly non-linearity of the problem space.
